Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-25 astronum_2017/astronum-amrex.tex
update some paper refs

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{summitdev_scaling}
\includegraphics[width=0.48\linewidth]{cori_scaling}
\caption{\label{fig:knl-gpu-scaling} \castro\ scaling on new
  architectures.  The left figure shows the \castro\ GPU proxy app
  (\starlord) on OLCF summitdev.  We see good scaling behavior to 64
  GPUs in this test of a pure hydro problem (Sedov w/ real EOS).  On the
right, we explore performance on NERSC Cori (and Intel Xeon Phi platform).}
\end{figure}

@@

Figure~\ref{fig:knl-gpu-scaling} shows the performance of
\starlord\ on the summitdev platform at OLCF\footnote{summitdev
  consists of 2 IBM Power8 processors and 4 Nvidia Pascal GPUs per
  node.}.  The highest GPU count (128) corresponds to 32 nodes on
summitdev.  We see a nearly linear speedup with the number of GPUs,
indicating good weak scaling on this machine.  Efforts are underway to
complete the port of the GPU developments into \castro.  This figure
also shows our performance on the Intel Xeon Phi manycore processors (using
NERSC Cori).  This is for the same problem as the self-gravity test on
Titan.  The Intel Xeon Phi chips in Cori
have 68 cores than can be run with 1, 2, or 4 hardware threads each.
For all these runs, we ran with 4 threads / core (272
threads / chip).

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{summitdev_scaling}
\includegraphics[width=0.48\linewidth]{cori_scaling}
\caption{\label{fig:knl-gpu-scaling} \castro\ scaling on new
  architectures.  The left figure shows the \castro\ GPU proxy app
  (\starlord) on OLCF Summitdev.  We see good scaling behavior to 64
  GPUs in this test of a pure hydro problem (Sedov w/ real EOS).  On the
right, we explore performance on NERSC Cori (and Intel Xeon Phi platform).}
\end{figure}

@@

Figure~\ref{fig:knl-gpu-scaling} shows the performance of
\starlord\ on the Summitdev platform at OLCF\footnote{Summitdev
  consists of 2 IBM Power8 processors and 4 Nvidia Pascal GPUs per
  node.}.  The highest GPU count (128) corresponds to 32 nodes on
Summitdev.  We see a nearly linear speedup with the number of GPUs,
indicating good weak scaling on this machine.  Efforts are underway to
complete the port of the GPU developments into \castro.  This figure
also shows our performance on the Intel Xeon Phi manycore processors (using
NERSC Cori).  This is for the same problem as the self-gravity test on
Titan.  The Intel Xeon Phi chips in Cori
have 68 cores than can be run with 1, 2, or 4 hardware threads each.
For all these runs, we ran with 4 threads / core (272
threads / chip).
